---
title: "Sarah R Cheat Sheet"
author: "Nicholas Piccaro"
date: "4/18/23"
output:
  html_document:
    toc: true
    theme: united
  pdf_document:
    toc: true
    theme: united
---
## Needs to be added
mean, median, sd

# What is R

R is an open-source programming language and environment for statistical computing and graphics. Widely used in data analysis, statistical modeling, and visualization, R offers a rich ecosystem of packages and has a large community of users and developers. Known for its flexibility, extensibility, and optimized syntax for data analysis, R is popular in academia, industry, and research for various applications such as data science, bioinformatics, finance, and social sciences.

#### R is a programming langage for statistics that uses packages to create an easy and powerful framework

# Different Data Types in R
Data types are the foundation of most coding languages. 
##Base R Data Types: 
```{r}
# Different data types in R
x <- 5  # Numeric
y <- "hello"  # Character
z <- TRUE  # Logical
a <- c(1, 2, 3)  # Vector
b <- list(1, "two", TRUE)  # List
c <- data.frame(x = 1:3, y = c("A", "B", "C"))  # Data frame

# Print the data types
cat("x| Numeric:", class(x), "\n")
cat("y| Character:", class(y), "\n")
cat("z| Logical:", class(z), "\n")
cat("a| Vector:", class(a), "\n")
cat("b| List:", class(b), "\n")
cat("c| Data frame:", class(c), "\n")
```

## Numeric Type Operations
What can we do with Numeric Data Types
### Basic Operations
```{r}
var1<-11 #A comment is a # in a code block this code wont run you can use it for notes
var2<-16
#above we assigned two variables var1 and var2 both of these are type numeric
```
### addition
```{r}
addV1V2 <- var1 + var2 # here we assign a new variable addV1V2 to the addition of var1 and var2
cat("var1+var2 = ", addV1V2, "\n") #we need to add ,"\n" so it prints on a newline
```

### subtraction
```{r}

subV1V2 <- var1 - var2 # here we assign a new variable subV1V2 to the subtration of var2 from var1
cat("var1-var2 = ", subV1V2, "\n")
```

### multiplication
```{r}
mulV1V2 <- var1 * var2 # here we assign a new variable mulV1V2 to the product of var2 and var1
cat("var1*var2 = ", mulV1V2, "\n")
```
### division
```{r}
divV1V2 <- var1 / var2 # here we assign a new variable divV1V2 to the division of var1 by var2
cat("var1/var2 = ", divV1V2, "\n")
```
### Exponentiation
```{r}
base <- 2
exponent <- 3
result <- base^exponent
print(result) # Output: 8
```

### Modulus
```{r}
dividend <- 10
divisor <- 3
remainder <- dividend %% divisor
print(remainder) # Output: 1
```

### Comparison
```{r}
a <- 5
b <- 10
less_than <- a < b
print(less_than) # Output: TRUE

greater_than_equal_to <- a >= b
print(greater_than_equal_to) # Output: FALSE

equality <- a == b
print(equality) # Output: FALSE
```

### Mathematical Functions
```{r}
x <- 9
square_root <- sqrt(x)
print(square_root) # Output: 3

absolute_value <- abs(-5)
print(absolute_value) # Output: 5

sine_value <- sin(pi/2)
print(sine_value) # Output: 1

natural_logarithm <- log(10)
print(natural_logarithm) # Output: 2.302585
```

## Character Type Operations
### Concatenation
```{r}
# Concatenation using paste()
first_name <- "John"
last_name <- "Doe"
full_name <- paste(first_name, last_name)
print(full_name) # Output: "John Doe"

# Concatenation using c()
greeting <- "Hello"
audience <- "world"
message <- c(greeting, audience)
print(message) # Output: "Hello" "world"

```

### Substring Extraction
```{r}
# Substring Extraction using substr()
text <- "Hello world"
substring <- substr(text, 1, 5)
print(substring) # Output: "Hello"

# Substring Extraction using []
substring <- text[7:11]
print(substring) # Output: "world"
```

### String Manipulation
```{r}
# String Manipulation
text <- "   R programming is fun!   "
length <- nchar(text)
print(length) # Output: 27

upper_text <- toupper(text)
print(upper_text) # Output: "   R PROGRAMMING IS FUN!   "

lower_text <- tolower(text)
print(lower_text) # Output: "   r programming is fun!   "

trimmed_text <- trimws(text)
print(trimmed_text) # Output: "R programming is fun!"
```

### Comparison Operators
```{r}
# Comparison
text1 <- "apple"
text2 <- "banana"
less_than <- text1 < text2
print(less_than) # Output: TRUE

equality <- text1 == text2
print(equality) # Output: FALSE
```

### Regular Expressions
```{r}
# Regular Expressions
text <- "The quick brown fox jumps over the lazy dog"
contains_fox <- grepl("fox", text)
print(contains_fox) # Output: TRUE

replaced_text <- gsub("fox", "cat", text)
print(replaced_text) # Output: "The quick brown cat jumps over the lazy dog"
```

## Boolean or Logical Type Operations

### Logical Operators

```{r}
# Logical Operators
x <- TRUE
y <- FALSE

# AND
result1 <- x & y
print(result1) # Output: FALSE

# OR
result2 <- x | y
print(result2) # Output: TRUE

# NOT
result3 <- !x
print(result3) # Output: FALSE

# Exclusive OR
result4 <- xor(x, y)
print(result4) # Output: TRUE
```

### Comparison Operators
```{r}
# Comparison Operators
a <- TRUE
b <- FALSE

equality <- a == b
print(equality) # Output: FALSE

inequality <- a != b
print(inequality) # Output: TRUE
```

### Conditional Statments
```{r}
# Conditional Statements
age <- 25
is_adult <- age >= 18

if (is_adult) {
  print("You are an adult.")
} else {
  print("You are not an adult.")
}

# Using ifelse()
result <- ifelse(is_adult, "You are an adult.", "You are not an adult.")
print(result) # Output: "You are an adult."
```

### Logical Functions
```{r}
# Logical Functions
x <- TRUE
y <- FALSE

is_logical <- is.logical(x)
print(is_logical) # Output: TRUE

is_true <- isTRUE(x)
print(is_true) # Output: TRUE

any_true <- any(x, y)
print(any_true) # Output: TRUE

all_true <- all(x, y)
print(all_true) # Output: FALSE
```

## Vector Operations

### Vector Creation

```{r}
# Creating a numeric vector
numeric_vector <- c(1.2, 2.3, 3.4, 4.5)
cat("numeric vector: ", numeric_vector ,"\n")

# Creating an integer vector
integer_vector <- c(1L, 2L, 3L, 4L)
cat("integer vector: ", integer_vector ,"\n")

# Creating a character vector
character_vector <- c("a", "b", "c", "d")
cat("character vector: ", character_vector ,"\n")
```

### Generate Vector Data
```{r}
# Create a vector of even numbers from 2 to 20
numbers2 <- seq(from = 2, to = 20, by = 2)
print(numbers2)
# Create a vector of random numbers between 0 and 1
numbers3 <- runif(n = 10)
print(numbers3)
```


### Vector Indexing
```{r}
# Accessing the first element of a vector
first_element <- numeric_vector[1]
cat("first element: ", first_element ,"\n")

# Accessing a range of elements
range_of_elements <- integer_vector[2:4]
cat("range_of_elements: ", range_of_elements,"\n")

# Accessing multiple elements using a vector of indices
multiple_elements <- character_vector[c(2, 4)]
cat("multiple_elements: ", multiple_elements ,"\n")
```

### Vector Arithmetic
```{r}
# Vector addition
sum_vector <- numeric_vector + integer_vector
cat("sum_vector: ", sum_vector ,"\n")

# Vector subtraction
diff_vector <- numeric_vector - integer_vector
cat("diff_vector: ", diff_vector,"\n")

# Vector multiplication
prod_vector <- numeric_vector * integer_vector
cat("prod vector: ", prod_vector,"\n")

# Vector division
quot_vector <- numeric_vector / integer_vector
cat("quot_vector: ", quot_vector,"\n")
```

### Vector Functions
```{r}
# Calculating the length of a vector
length_vector <- length(numeric_vector)
cat("length of vector: ", length_vector ,"\n")

# Finding the maximum value in a vector
max_value <- max(numeric_vector)
cat("max value of vector: ", max_value,"\n")

# Calculating the sum of all elements in a vector
sum_of_elements <- sum(numeric_vector)
cat("fsum of elements: ", sum_of_elements,"\n")

# Applying a function to each element of a vector
sqrt_vector <- sqrt(numeric_vector)
cat("sqrt of vector: ", sqrt_vector ,"\n")
```
### Vector Comparison
```{r}
# Comparing two vectors element-wise
comparison_vector <- numeric_vector > integer_vector
cat("comparison vector: ", comparison_vector ,"\n")
# Checking if all elements of a vector are equal
all_equal <- all(numeric_vector == integer_vector)
cat("all equal: ", all_equal,"\n")
# Checking if any element of a vector satisfies a condition
any_satisfy <- any(numeric_vector > 3)
cat("satisfy condition: ", any_satisfy ,"\n")
```

## List Operations

### List Creation
```{r}
# Creating a list with named elements
my_list <- list(a = 1, b = "hello", c = c(1.2, 2.3, 3.4))

# Creating a list with unnamed elements
my_list <- list(1, "hello", c(1.2, 2.3, 3.4))
```

### List Indexing
```{r}
# Accessing a list element using single brackets
list_element <- my_list["a"]

# Accessing a list element using double brackets
list_element <- my_list[["a"]]
```

### List Manipulation
```{r}
# Adding an element to a list
my_list$c <- 3.14

# Removing an element from a list
my_list$d <- NULL

# Modifying an element in a list
my_list$a <- 10
```

### List Functions
```{r}
# Checking the length of a list
list_length <- length(my_list)

# Checking the names of list elements
list_names <- names(my_list)

```

### List Unlisting
```{r}
# Converting a list to a vector
my_vector <- unlist(my_list)
```

### List iteration
```{r}
# Iterating over list elements with a for loop
for (i in 1:length(my_list)) {
  print(my_list[[i]])
}

# Iterating over list elements with lapply()
lapply(my_list, function(x) print(x))
```

## Data Frame Operations

### Creating a Data Frame
```{r}
# Creating a data frame
df <- data.frame(
  Name = c("John", "Jane", "Alice", "Bob"),
  Age = c(25, 30, 22, 35),
  Height = c(6.1, 5.5, 5.9, 5.7),
  Married = c(FALSE, TRUE, FALSE, TRUE),
  Weight = c(180, 150, 140, 160),
  stringsAsFactors = FALSE
)

# Printing the entire data frame
print(df)
```

### Accessing Column from DataFrame
```{r}
# Access the age column of the data frame
df_age <- df$Age
print(df_age)
```

### Getting Frequency of Categorical Variables in DataFrame
```{r}
# Use the table() function to get the frequency of each true and false
marry_freq <- table(df$Married)

# Print the frequency table
print(marry_freq)
```


### Subsetting DataFrame
```{r}
# Subset data frame to get rows where Age is greater than 25
df_subset <- df[df$Age > 25, ]
print(df_subset)
```

### Adding New Columns
```{r}
# Add a new column "BMI" calculated from Height and Age
df$BMI <- df$Weight / (df$Height^2)
print(df)
```

### Changing Data Types
```{r}
# Convert Age column to a factor
df$Age <- as.factor(df$Age)
print(df)
```

### Sorting Data
```{r}
# Sort data frame by Age in ascending order
df <- df[order(df$Age), ]
print(df)
```

### Aggregating Data
```{r}
# Calculate mean Height and Age by Married status
library(dplyr)
df_summary <- df %>% 
  group_by(Married) %>% 
  summarize(mean_Height = mean(Height), mean_Age = mean(Age))
print(df_summary)
```


# Matrices

## Creating a Matrix
```{r}
# Creating a matrix
mat <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3)
print(mat)
```

## Matrix Arithmetic
```{r}
# Matrix addition
mat1 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3)
mat2 <- matrix(c(6, 5, 4, 3, 2, 1), nrow = 2, ncol = 3)
mat_sum <- mat1 + mat2
print(mat_sum)

# Matrix multiplication
mat_prod <- mat1 %*% t(mat2)  # Note: %*% is used for matrix multiplication, t() is used for transposition
print(mat_prod)
```

## Matrix Indexing
```{r}
# Accessing elements of a matrix
element <- mat[1, 2]  # Access element in the first row and second column
print(element)

# Accessing rows and columns of a matrix
row <- mat[1, ]  # Access the first row
col <- mat[, 2]  # Access the second column
print(row)
print(col)
```

## Matrix Manipulation
```{r}
# Combining matrices
mat1 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3)
mat2 <- matrix(c(6, 5, 4, 3, 2, 1), nrow = 2, ncol = 3)
mat_combined <- cbind(mat1, mat2)  # Combine matrices by column
print(mat_combined)

# Extracting diagonal elements
diag_elements <- diag(mat1)  # Extract diagonal elements of a matrix
print(diag_elements)
```

# Reading in CSV type data
### Using the Camera Data set

```{r}
# Read a CSV file with additional parameters
cameraData <- read.csv("camera_dataset.csv", header = TRUE, sep = ",", encoding = "UTF-8", na.strings = "NA")

head(cameraData)
```

# Data Exploration

## Structure of Data
We see that this data has 13 variables: Model, release date, max resolution, low resolution, effective pixels, zoom wide, zoom tele, normal focus, macro focus, storage included, weight, dimensions, and price
```{r}
str(cameraData)
```

## Summarize Data
This displays the quartile data of all the columns of the Data frame
```{r}
summary(cameraData)
```

## Check first few rows of Data
```{r}
# Check the first few rows of the dataset
head(cameraData)
```

## Check missing values
we see some of the fields have missing values, its ultimate up to us how we want to handle missing data. We could remove the data, we could just leave it, we could set it to the mean. Generally if the data is big enough removing it is sufficient.
```{r}
sapply(cameraData, function(x) sum(is.na(x)))
```

## Remove missing values from dataframe
There are several ways to use this
```{r}
camera_clean <- na.omit(cameraData)
```
## Renaming Data Frame Column Names
```{r}
# Assign new column names
colnames(camera_clean) <- c('Model', 'ReleaseDate', 'MaxResolution', 'LowResolution', 'EffectivePixels', 'ZoomWide', 'ZoomTele', 'NormalFocusRange', 'MacroFocusRange', 'Storage', 'Weight','Dimensions', 'Price')

head(camera_clean)
```

## Adding New Column to DataFrame
```{r}
library(tidyverse)

# Extract the first word from the 'strings' column
camera_clean <- camera_clean %>% mutate(Brand = str_extract(Model, "\\b\\w+"))

# View the dataframe with the new 'first_word' column
head(camera_clean)
```


# Useful Packages

## GGPLOT2 for plotting
### Importing GGPLOT2
```{r}
library(ggplot2)
```
### Scatter Plot
```{r}
ggplot(camera_clean, aes(x = EffectivePixels, y = Price)) +
  geom_point() +
  labs(x = "Effective Pixels", y = "Price") +
  ggtitle("Price vs. Effective Pixels")
```

###  Bar Chart
```{r}
# Bar chart of number of cameras by brand
ggplot(camera_clean, aes(x = ReleaseDate, fill = ReleaseDate)) +
  geom_bar() +
  labs(x = "Release Date", y = "Count") +
  ggtitle("Number of Cameras Released Every Year") +
  theme(legend.position = "none")
```

```{r}
# Bar chart of number of cameras by brand
ggplot(camera_clean, aes(x = Brand, fill = Brand)) +
  geom_bar() +
  labs(x = "Brand", y = "Count") +
  ggtitle("Number of Cameras by Brand") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
```

### Line Plot
```{r}
ggplot(camera_clean, aes(x = ReleaseDate, y = Price, color = Brand)) +
  geom_line(stat = "summary", fun = "mean") +
  labs(x = "Year", y = "Average Price") +
  ggtitle("Average Price of Cameras by Brand")
```

### BoxPlot
```{r}
# Box plot of price by Brand note this has a log applied to the y axis to change the appearance
ggplot(camera_clean, aes(x = Brand, y = Price, fill = Brand)) +
  geom_boxplot() +
  labs(x = "Type", y = "Price") +
  ggtitle("Price Distribution by Camera Type")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(trans = "log10")
```
### Line of Best Fit through scatter plot
```{r}
# Scatter plot with line of best fit
ggplot(camera_clean, aes(x = MaxResolution, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +  # Add line of best fit
  labs(x = "Max Resolution", y = "Price") +
  ggtitle("Scatter Plot of Price vs. Max Resolution with Line of Best Fit")+
  scale_y_continuous(trans = "log10")
```


## DPLYR for data manipulation
### Import DPLYR
```{r}
library(dplyr)
```

### Filter Data
```{r}
# Filter the data frame to include only rows where the Brand is "Canon"
canon_cameras <- camera_clean %>% 
  filter(Brand == "Canon") %>% 
  select(Model, Price)

# Display the filtered data frame
head(canon_cameras) #canon_cameras is a new dataframe with only canon cameras and the price
```
### Grouping by specific column names and summarize
```{r}
# Group the data frame by Brand and calculate the average Price for each Brand
brand_avg_price <- camera_clean %>% 
  group_by(Brand) %>% 
  summarize(AveragePrice = mean(Price, na.rm = TRUE))

# Display the summarized data frame
head(brand_avg_price) # brand_avg_price is a new data frame with the brands and the average price
```

### Sort and Arrange Data Frame
```{r}
# Sort the data frame by Price in descending order
sorted_cameras <- camera_clean %>% 
  arrange(desc(Price))

# Display the sorted data frame
head(sorted_cameras)
```



## TIDYR for cleaning or tidying data

###Load TIDYR
```{r}
library(tidyr)
```

### Handle missing values
```{r}
missing_values <- cameraData %>% 
  is.na() %>% 
  colSums()

# Display the columns with missing values and their corresponding counts
missing_values

# Remove rows with missing values in the Price column
camera_df <- cameraData %>% 
  drop_na(Storage.included)

# Fill in missing values in the Megapixels column with the mean Megapixels value
camera_df <- camera_df %>% 
  fill(Weight..inc..batteries. , .direction = "down")

# Display the updated data frame
head(camera_df)
```

### Reshape Data
```{r}
# Convert the data frame from wide to long format
camera_df_long <- camera_df %>% 
  pivot_longer(cols = c(Effective.pixels, Price), 
               names_to = "Variable", 
               values_to = "Value")

# Display the reshaped data frame
head(camera_df_long)
```

### Clean Data
```{r}
# Replace "0" values in the Weight column with NA
camera_df <- cameraData
camera_df <- camera_df %>% 
  mutate(Weight..inc..batteries. = ifelse(Weight..inc..batteries. == 0, NA, Weight..inc..batteries.))

# Replace all spaces in the Model column with underscores
camera_df <- camera_df %>% 
  mutate(Model = gsub(" ", "_", Model))

# Display the cleaned data frame
head(camera_df)
```

### Convert Data from Long to Wide Format
```{r}
# Convert the data frame from long to wide format
camera_df_wide <- camera_df_long %>% 
  pivot_wider(names_from = "Variable", 
              values_from = "Value")

# Display the spread data frame
camera_df_wide
```
#Simple Tests

## Frequency of Variables
```{r}
# Create a vector of categorical videos
videos <- c("Funny", "Music", "Sports", "News", "Funny", "Music", "Sports", "Music")

# Use the table() function to get the frequency of each category
video_freq <- table(videos)

# Print the frequency table
print(video_freq)
```

## Mean
```{r}
numbers <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
mean(numbers)
```

## Median
```{r}
median(numbers)
```

## Standard Deviation
```{r}
sd(numbers)
```



# Statistical Tests
## One Sample T-Test
```{r}
# One-sample t-test to compare mean Price to a hypothesized value of $500
t.test(camera_clean$Price, mu = 500)
```
## Paired Samples T-Test
```{r}
# Paired samples t-test to compare mean Low Resolution to Max Resolution
t.test(camera_clean$LowResolution, camera_clean$MaxResolution, paired = TRUE)
```


## Two or Independent Sample T-Test
Two-Sample T-Test: The t.test() function is used to compare the means of two groups. The result of the t-test provides a p-value, which is used to determine if there is statistically significant evidence to reject the null hypothesis that the means of the two groups are equal. A low p-value (typically less than 0.05) suggests that there is evidence to support the conclusion that the means of the two groups are different.
```{r}
# Two-sample t-test to compare Price between Brand A and Brand B
t.test(Price ~ Brand, data = camera_clean, subset = Brand %in% c("Canon", "Sigma"))
```
## Chi Square Test
Chi-Square Test: The chisq.test() function is used to test the independence between two categorical variables. The result of the chi-square test provides a p-value, which is used to determine if there is statistically significant evidence to reject the null hypothesis of independence between the two variables. A low p-value (typically less than 0.05) suggests that there is evidence to support the conclusion that the two categorical variables are associated or dependent.
```{r}
# Chi-square test for independence between Resolution and Brand
chisq.test(camera_clean$MaxResolution, camera_clean$Brand)
```

## Correlation Test
Correlation Test: The cor.test() function is used to test the association between two continuous variables. The result of the correlation test provides a correlation coefficient (typically Pearson's correlation coefficient), which indicates the strength and direction of the association between the two variables, as well as a p-value to determine if the association is statistically significant. A correlation coefficient close to 1 or -1 indicates a strong association, while a coefficient close to 0 indicates a weak or no association. A low p-value (typically less than 0.05) suggests that there is evidence to support the conclusion that the two continuous variables are correlated.
```{r}
# Correlation test between Price and Max Resolution
cor.test(camera_clean$Price, camera_clean$MaxResolution)
```

## One Way ANOVA
One-Way ANOVA: The aov() function is used to compare means across multiple groups. The result of the one-way ANOVA provides an F-statistic and a p-value, which are used to determine if there is statistically significant evidence to reject the null hypothesis that the means of all groups are equal. A high F-statistic and a low p-value (typically less than 0.05) suggest that there is evidence to support the conclusion that there are statistically significant differences among the means of the groups.
```{r}
# One-way ANOVA to compare Price across different Brand categories
model <- aov(Price ~ Brand, data = camera_clean)
summary(model)
```

# Regression Tests

## Simple Linear Regression
The output includes coefficients, standard errors, t-values, p-values, and goodness of fit statistics, which provide information about the estimated coefficients, significance of the coefficients, goodness of fit of the models, and statistical significance of the relationships between the independent and dependent variables.
```{r}
# Simple Linear Regression
# Fit a simple linear regression model with Price as the dependent variable and MaxResolution as the independent variable
simple_reg_model <- lm(Price ~ MaxResolution, data = camera_clean)

# Print the summary of the simple linear regression model
summary(simple_reg_model)
```

## Mutliple Linear Regression
```{r}
multiple_reg_model <- lm(Price ~ MaxResolution + Brand + ZoomWide, data = camera_clean)

# Print the summary of the multiple linear regression model
summary(multiple_reg_model)
```

## Poison Regression
```{r}
# Poisson Regression
# Fit a Poisson regression model with Price as the dependent variable and EffectivePixels, ZoomWide, and Brand as independent variables
poisson_model <- glm(Price ~ EffectivePixels + ZoomWide + Brand, data = camera_clean, family = poisson)

# Print the summary of the Poisson regression model
summary(poisson_model)
```


# Regression Example with Prediction

## Split Data into Training and Testing
We use the caret package for splitting into training and testing its easy
```{r}
camera_clean_example = subset(camera_clean, select = -c(Model)) #we remove the Model attribute here
# Load the caret package
library(caret)

# Set the seed for reproducibility
set.seed(123)

# Split the data into training and testing sets
train_indices <- createDataPartition(y = camera_clean_example$Price, p = 0.9, list = FALSE)
trainCamera <- camera_clean_example[train_indices, ]
testCamera <- camera_clean_example[-train_indices, ]
```
## Training the Model
Lets see if we can predict the brand of the Price based on all the  of the camera except model
```{r}
# Simple Linear Regression Using the training data
test_model <- lm(Price ~ Brand + ReleaseDate + MacroFocusRange , data = trainCamera) 

# Print the summary of the simple linear regression model
summary(test_model)
```
## Predicting Price
```{r}
# Perform prediction using the linear regression model on the test data
predicted_prices <- predict(test_model, newdata = testCamera)
# Store predicted prices in a named numeric vector
predicted_prices <- as.vector(predicted_prices)
sum(predicted_prices)
```
## Evaluating Accuracy
```{r}
# Calculate the accuracy of the predictions
actual_prices <- testCamera$Price
actual_prices <- as.vector(actual_prices)
accuracy <- mean(abs(predicted_prices - actual_prices)/actual_prices)

# Print the accuracy
cat("Accuracy:", accuracy, "\n")
```
In short this model is terrible
